\RequirePackage{fix-cm}
\PassOptionsToPackage{unicode, psdextra}{hyperref}
\documentclass[sn-mathphys-num, pdflatex, referee]{sn-jnl}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm, amsfonts}
\usepackage{booktabs}
\usepackage{tocloft}
\usepackage{xcolor}
\usepackage{bookmark} % This loads hyperref automatically in sn-jnl

% This block overrides the Springer default "hidelinks" setting
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Recursive Rounding Guide},
}

% Optional: Force the URL style to be the same as the surrounding text
\urlstyle{same}
\raggedbottom
\setlength{\cftaftertoctitleskip}{20pt} % Adjust this number to increase the gap
% 4. Enable Subsection Numbering (e.g. 3.1, 3.2)
\setcounter{secnumdepth}{2} 
\usepackage{cite}

% Theorem Styles
\newtheorem{theorem}{Theorem}[section]
\usepackage{mdframed}
\usepackage{listings}
\usepackage{array}
\usepackage{tikz}
\usetikzlibrary{positioning, arrows.meta}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}

% This isolates the font state completely before building the hyperlink
\newcommand{\gterm}[2]{\begingroup\normalfont\scshape\hyperlink{#1}{#2}\endgroup}
% --- Custom Sidebar Environment ---
\newmdenv[
  linewidth=1pt,
  frametitlefont=\bfseries,
  frametitleaboveskip=8pt,
  frametitlebelowskip=8pt,
  innertopmargin=10pt,
  innerbottommargin=10pt,
  innerleftmargin=10pt,
  innerrightmargin=10pt,
  roundcorner=5pt,
  nobreak=true  % <--- ADD THIS LINE
]{sidebar}
% --- Code Listing Style for Appendix ---
\lstset{
  basicstyle=\small\ttfamily,
  frame=single,
  breaklines=true,
}
\newcommand{\glink}[2]{\hyperref[gloss:#1]{#2}}

% --- Title Information ---
\title[Recursive Rounding]{Guide to the ``Recursive Rounding: A Constructive Proof of the Riemann Hypothesis''}

\author*[1]{\fnm{James E.} \sur{Rock}}
\email{jimrock69@comcast.net}

\affil[1]{\orgname{Independent Researcher}, \orgaddress{\street{5689 Dartmouth Ct.}, \city{Ypsilanti}, \state{MI}, \postcode{48197}, \country{USA}}\\ \text{ORCID: 0000-0003-2858-6077}}

\begin{document}
\maketitle 

\hypersetup{
    citecolor=black,       % Forces citation links to be black
    urlcolor=black,        % Forces external web links to be black
    pdfauthor={James E. Rock},
    pdftitle={Guide to the Recursive Rounding Proof},
    bookmarksnumbered=true % Numbers the bookmarks in the PDF sidebar
}

\maketitle

\begin{abstract}
{ }This technical guide serves as a comprehensive companion to the manuscript, "Recursive Rounding: A Constructive Proof of the Riemann Hypothesis," providing an expository bridge between the rigorous formal verification and the underlying geometric intuition. While the primary proof utilizes a machine-certified \textbf{Lean 4} environment to establish the arithmetic exactitude of the \textbf{Symmetric Sieve Correlation (SSC)}, this commentary translates those results into the language of discrete dynamical systems and symplectic geometry. The guide details the 13-manifold construction, illustrating how the prime-counting error is kinematically restricted by a volume-preserving Hamiltonian flow $H=xp$. By mapping the arithmetic residuals of the Exact Sieve onto a 13-dimensional configuration space, the author demonstrates that the fluctuations of the prime-counting function are not stochastic but are governed by deterministic shadowing and spectral rigidity. Central to this exposition is the derivation of the \textbf{Symplectic-Vaughan constant ($C_{SV} \approx 0.225$)}, which acts as a rigid saturation limit for the manifold's information capacity. Ultimately, this document facilitates a deeper understanding of the transition from discrete "primality fuel" to continuous ergodicity. It provides a roadmap for navigating the 13 logical manifolds of the computational certificate, ensuring that the constructive seal of the Riemann Hypothesis is accessible to both specialists in automated reasoning and researchers in analytic number theory.
\end{abstract}

\tableofcontents

% --- SECTION 1 ---
\section{Introduction: }

\textit{Guidance: This section traces the foundations of the proof. Note: Every term in} \textsc{Small Caps} \textit{is a clickable link to the Glossary in Appendix A, which provides a technical definition and traces its specific utility in the primary Proof.}
\subsection{Purpose of this Document}
The primary document ''Recursive Rounding: A Constructive Proof of the Riemann Hypothesis'' is available in a public repository:  

\noindent \href{https://github.com/jimrock69/RH-Constructive-Certificate}{\color{blue}{https://github.com/jimrock69/RH-Constructive-Certificate}}. It establishes the \gterm{sv_bound}{Symplectic-Vaughan Bound} using the formalisms of \gterm{geometry}{Symplectic Geometry} and \gterm{spectral}{Spectral Rigidity}. This guide is intended as an aid to grasping the novel interdisciplinary connections in the primary manuscript. It contains a summary of common objections that might be made along with responses. It should also help non-experts who want a better grasp of the paper's mathematics.  \textit{Formatting Note:} To maintain the narrative flow of this expository guide, formal bibliographic citations have been omitted. All formal references, historical citations, and proofs of cited theorems (e.g., Gromov's Non-Squeezing Theorem, Weyl's Equidistribution Theorem) are fully documented in the bibliography of the primary manuscript.

\subsection{The Core Problem: The Staircase vs. The Curve}
At its heart, the \gterm{rh}{Riemann Hypothesis} is a problem about measurement error.
\begin{itemize}
    \item \textbf{The Reality:} The count of primes is a discrete step function, often called the ``Staircase.''
    \item \textbf{The Prediction:} The Logarithmic Integral ($\text{Li}(x)$) is a smooth, continuous curve.
\end{itemize}
The difference between them is the \gterm{error_term}{Error Term ($E(x)$)}. Riemann conjectured that if this error remains tightly bounded---because the zeros of the \gterm{zeta}{Riemann Zeta Function} are confined to the \gterm{critical_line}{Critical Line}---the hypothesis is true.
The Master Document identifies this bound as the \gterm{csv}{Symplectic-Vaughan Constant} ($C_{SV}$).
\subsection{The Four Pillars of the Proof}
The structural integrity of this proof rests on four foundational pillars. Together, they transform the study of prime distribution from a probabilistic estimation into a \textit{deterministic dynamical system}.

\begin{enumerate}
    \item \textbf{Constructive Recursion (The Lossless Sieve)}
    We define the prime-counting function $\pi(x)$ through an \gterm{exact_sieve}{Exact Sieve}. Unlike classical approaches that approximate counts via prime truncation or smoothing, our recursion retains every floor-function residual. By refusing to discard the ``quantization noise,'' we preserve the full information density of the integer line.
  
    \noindent\textit{Transition:} By strictly preserving the quantization error rather than smoothing it away, the arithmetic of the sieve is mathematically forced to obey conservation laws. This lossless retention acts as the essential bridge from pure arithmetic to our second pillar: symplectic geometry.
    
    \item \textbf{Symplectic Constraint (The Incompressible Flow)}
    This pillar provides the geometric justification for the $O(\sqrt{x}\ln x)$ bound, answering the fundamental question: \textit{Why is the error term not a Random Walk?}
    
    Standard heuristics (e.g., the Cramér Model) model primes as a diffusive gas, implying entropy must increase and variance may drift unboundedly. We prove the \gterm{exact_sieve}{Exact Sieve} is a \textit{conservative mechanical system}. Under \gterm{liouville}{Liouville's Theorem}, the sifting transformation has a Jacobian determinant of exactly 1, preserving phase-space volume.     
        
    \textbf{The Confinement:} Like an incompressible fluid in a sealed container, the sieve residuals can be deformed (via the scaling $x \to x/n$), but they cannot expand. This geometric rigidity confines the error trajectory to a fixed energy surface---the \gterm{m13}{13-Manifold}---prohibiting the ``stochastic drift'' permitted by probabilistic models.
   
    \noindent\textit{Transition:} While this symplectic constraint guarantees the error cannot expand indefinitely, it does not describe its internal dynamics. To understand how the signal navigates within this topologically confined phase space without localized clustering, we must transition from macroscopic geometry to ergodic theory.
    
    \item \textbf{Ergodicity (Uniform Distribution of Phases)}
    To justify the transition from discrete path-averages to continuous variance, we apply the \gterm{weyl}{Kronecker-Weyl Theorem}. Because the logarithms of the primorial base $\mathcal{P}_{12}$ are linearly independent over $\mathbb{Q}$, the quantization residuals do not cluster or interfere constructively. Instead, they define a dense, \gterm{ergodic}{ergodic trajectory} that converges to the uniform \gterm{haar}{Haar measure} on the torus $\mathbb{T}^{12} \times \mathbb{R}^+$. This ensures the variance is exactly $\sigma^2 = 1/12$.

    \noindent\textit{Transition:} Having established that the error trajectory is both geometrically confined by the \gterm{hamiltonian}{Hamiltonian flow} and uniformly distributed across the torus, we arrive at the final architectural requirement: quantifying the absolute physical capacity of this saturated manifold.

    \item \textbf{spectral rigidity} (The 13-Manifold Saturation)
    The final pillar derives the system's capacity by invoking the duality between spectral density and phase space geometry. We identify the \gterm{m13}{13-Manifold} as the minimal stable embedding required to host the 12 independent frequencies ($\ln p_i$) of the primorial base $\mathcal{P}_{12}$. Because \gterm{geometry}{symplectic geometry} necessitates that these degrees of freedom be coupled, the 12 prime frequencies are geometrically anchored as \textit{6 symplectic conjugate planes} (canonical position-momentum pairs). These 12 discrete dimensions, coupled with a 13th continuous global translation parameter representing the number line itself, define the configuration space. The error term possesses \gterm{spectral}{Spectral Rigidity}; it is geometrically forced to saturate at the symplectic capacity limit of this manifold. This is the geometric manifestation of the \gterm{action_quantum}{Action Quantum} ($\mathcal{A}_{min} = 1/2\pi$), which dictates that the information density cannot be compressed below a fundamental threshold.
\end{enumerate}
    \subsection{Mechanization (Vertical Verification and Boolean Reflection)} 
    This translates the geometric constraints into a machine-checked formal proof. It answers the critical verification question: \textit{How do we map continuous symplectic geometry into the discrete type-theory of Lean 4?}

    Standard theorem provers face immense computational overhead when attempting to natively process infinite, non-compact continuous spaces. To bridge this gap without sacrificing rigor, we employ a ``Vertical Verification'' architecture. 

\begin{itemize}
    \item \textbf{The Axiomatic Container:} We explicitly partition the classical continuous geometry from the computable discrete bounds. Foundational analytic truths (such as Liouville's measure preservation) form a strictly defined Trusted Computing Base. 
    \item \textbf{Boolean Reflection:} With the geometric container locked in as an axiomatic boundary, the Lean 4 computational kernel is deployed to rigorously evaluate the discrete arithmetic of the Exact Sieve. Using the \texttt{native\_decide} \ref{BF} tactic, the kernel computes the exact combinatorial bounds and formally reflects the boolean result back into the type theory. 
\end{itemize}

\textit{Transition:} This elevates the manuscript from a theoretical mathematical framework to a computational certificate. It proves that the discrete sifting trajectory is mechanically verified to never breach the continuous geometric capacity limit.


\subsection{Methodological Defense: Why Symplectic Geometry?}

\textit{Guidance: This section provides the core arguments justifying the shift from classical Analytic Number Theory to the 13-Manifold framework.}

\noindent \textbf{The Failure of Randomness (Why change tools?)} \\
\noindent \textbf{The Critique:} Primes are often modeled as random coin tosses with probability $P \approx 1/\ln x$. 

\textbf{The Defense:} Primes are strictly determined by the arithmetic of division, not chance. Random models permit infinite drift, but the integers are rigid. We utilize \gterm{ergodic}{Ergodic Theory} and \gterm{geometry}{Symplectic Geometry} because they are the native languages of deterministic systems that exhibit pseudo-random behavior while remaining strictly bounded.

\noindent \textbf{The Discovery of the Manifold (Why 13 Dimensions?)} \\
\textbf{The Critique:} Applying \gterm{hamiltonian}{Hamiltonian mechanics} to the Sieve of Eratosthenes appears arbitrary.

\textbf{The Defense:} The geometry was not forced; it was revealed. The \gterm{exact_sieve}{Exact Sieve} is a \textbf{lossless compression algorithm}. Compressing the position space ($x/n$) necessitates a reciprocal expansion in the momentum space ($np$) to conserve the total state. This conservation---shown by the Jacobian determinant ($\det(J)=1$), indicating the volume is preserved---is the literal definition of a symplectic mapping. 

The \gterm{m13}{13-Manifold} ($\mathbb{T}^{13}$) is the specific configuration space required to prevent ``spectral overlap'' between the 12 frequencies of $\mathcal{P}_{12}$, ensuring the stability of the \gterm{csv}{Symplectic-Vaughan Bound}. This $(12+1)$ architecture is anchored by the \gterm{reeb}{Reeb vector field}, which represents the continuous flow of the number line itself, while the 12 discrete prime frequencies define the transverse symplectic hyperplanes of the phase space.

% --- SECTION 2 ---
\section{The Proof Architecture: A Roadmap}

\textit{Guidance: Before diving into the mechanics, we visualize the structural dependency of the argument to ensure the logic is linear and constructive.} 

\subsection{The Logic Map}
An expert reader can trace the proof's dependency chain as follows:
\begin{itemize}
    \item \textbf{Section 3 (\gterm{deterministic}{Deterministic Mechanism}):} Rejects probability; establishes the \gterm{ergodic}{Ergodic} nature of the primes.
    \item \textbf{Section 4 (The Engine):} Defines the ``Experiment'' (\gterm{exact_sieve}{Exact Sieve}) and the ``Noise'' (\gterm{floor_function}{Floor Function}).
    \item \textbf{Section 5 (The Analytics):} Establishes the \gterm{hamiltonian}{Hamiltonian} system is volume preserving.
    \item \textbf{Section 6 (The Geometry):} Builds the ``Container'' (\gterm{phase_space}{Phase Space}) that traps the signal.
    \item \textbf{Section 7 (The Limit):} Measures the container to derive the \gterm{csv}{Symplectic-Vaughan Constant}.
    \item \textbf{Section 8 (Conclusion):} Satisfaction of \gterm{von_koch}{Von Koch Criterion}.
\end{itemize}

\subsection{The Linearity Guarantee (Anti-Circularity)}
A common pitfall in Riemann Hypothesis proofs is circularity. We provide the following guarantee:
\begin{quote}
``This proof is strictly constructive. We never assume the location of the \gterm{zeta}{Zeta zeros}. We start solely with the properties of the \gterm{floor_function}{floor function} and derive the bound \gterm{csv}{$C_{sv}$}  from geometric first principles. The \gterm{rh}{Riemann Hypothesis} is a \textit{consequence} of this bound, not an input.''
\end{quote}
% --- SECTION 3 
\section{The Deterministic Mechanism}
\label{sec:mech}

\textit{Guidance: This section establishes the context. The primes are not random.} 

\subsection{The ``Coin Flip'' Fallacy and Black Swans}
Harald Cramér hypothesized that primes behave randomly, like coin flips occurring with a probability of ($P \approx 1/\ln x$). While this predicts averages well, it fails as a proof because probability admits the possibility of ``Black Swan'' events (large deviations). 

A famous example is \textbf{Skewes' Number}---a point where the prime count unexpectedly crosses the estimate, violating simple probabilistic intuition. A rigorous proof requires absolute certainty that no such violation explodes to infinity.

\subsection{The ``Clockwork'' Reality}
We rely on \gterm{deterministic}{Determinism}. When the \gterm{exact_sieve}{Exact Sieve} divides an integer $n$ by a prime $p$, the remainder is not random---it is forced. The division remainders for the primes are \textbf{``meshed'' together} by the arithmetic rigidity of the integers. The system behaves like a giant set of interlocking gears, not a bag of loose coins.

\subsection{The ``Spirograph'' Effect (Incommensurate Periods)}
What prevents the errors from piling up? The answer lies in the linear independence of prime logarithms. Imagine a complex Spirograph Fig \ref{fig:spirograph}.

Because the primes are fundamentally distinct, the logarithms of the primorial base $\mathcal{P}_{12}$ (i.e., $\ln 2, \ln 3, \dots, \ln 37$) are linearly independent over $\mathbb{Q}$. In mechanical terms, the ``gears'' of the \gterm{exact_sieve}{Exact Sieve} possess strictly incommensurate periods. They never synchronize to form a resonant, localized loop. 

The assertion that these gears never synchronize is not a metaphor; it is an algebraic certainty derived from the Fundamental Theorem of Arithmetic. If the logarithms were linearly dependent, there would exist integers $c_i$ such that $\sum c_i \ln p_i = 0$. Exponentiating this would imply $\prod p_i^{c_i} = 1$, which directly contradicts the unique factorization of integers.

\subsubsection*{Technical Insight: The Contact Manifold $\mathcal{M}_{13}$}
While the standard heuristic might visualize this as a simple shape, our formal framework anchors this mechanism to the precise geometry of the contact manifold: $\mathcal{M}_{13} = \mathbb{T}^{12} \times \mathbb{R}^+$. The system splits into two distinct operational roles:
\begin{itemize}
    \item \textbf{The Gears ($\mathbb{T}^{12}$):} The 12 linearly independent prime frequencies define the transverse symplectic hyperplanes: the ``geometric arena'' where these gears spin. They act as the incommensurate, rotating parts that generate the sieve's structural phases.  
    \item \textbf{The Flow ($\mathbb{R}^+$):} The 13th dimension acts as the \gterm{reeb}{Reeb vector field}. The \textit{Reeb flow} is the physical ``time'' or ``forward momentum,'' representing the continuous progression of the number line $x$ that drives the entire system forward.
\end{itemize}

This arithmetic rigidity forces the error trajectory to be dense and strictly \gterm{ergodic}{Ergodic} across the configuration space. By \gterm{weyl}{Weyl's Equidistribution Theorem}, the trajectory of these combined phases traces a uniform, non-repeating web across the transverse symplectic space $\mathbb{T}^{12}$, stabilized by the continuous \textit{Reeb flow}. The signal never retraces the exact same path, ensuring the errors visit positive and negative bounds with uniform frequency modulo 1. Because the phases destructively interfere rather than stacking constructively, the error is geometrically prohibited from accumulating into a ``Black Swan'' event.

%\begin{sidebar}[frametitle={Technical Insight: The 13th Dimension}]
While the 12 primes provide the incommensurate ``gears,'' the 13th dimension is defined by the continuous flow of the number line $x$. This $(12+1)$ configuration is what defines the \gterm{m13}{13-Manifold} verified in Section 7.0 of the Lean certificate. The arithmetic rigidity forces the error trajectory to be dense on the torus $\mathbb{T}^{12} \times \mathbb{R}^+$, ensuring ergodicity.
%\end{sidebar}

\gterm{weyl}{Weyl's Equidistribution Theorem} guarantees that the trajectory of these combined phases traces a dense, uniform web across the torus, never retracing the same line twice.

\begin{figure}[ht]
\centering
\begin{tikzpicture}[scale=0.8]
    % Define the spirograph parameters
    \def\R{3}    % Radius of big circle
    \def\r{1.05} % Radius of small moving circle
    \def\d{2.4}  % Distance of pen from center of small circle
    
    % Draw the "Constraint" (The Unit Circle / Torus)
    \draw[thick, gray!30] (0,0) circle (\R);
    
    % Draw the Spirograph Path
    \draw[domain=0:20, samples=600, variable=\t, opacity=0.8] 
        plot ({(\R-\r)*cos(\t*360) + \d*cos((\R-\r)/\r*\t*360)}, 
              {(\R-\r)*sin(\t*360) - \d*sin((\R-\r)/\r*\t*360)});
    
    % Annotations
    \node[align=center] at (0, -4.5) {\textbf{The Ergodic Web}};
    \node[align=center, font=\small] at (4, 2) {Trajectory never\\repeats due to\\Linear Independence};
    
    % Dotted line showing the "next" path
    \draw[blue!40, dashed, domain=20:22, samples=100, variable=\t] 
        plot ({(\R-\r)*cos(\t*360) + \d*cos((\R-\r)/\r*\t*360)}, 
              {(\R-\r)*sin(\t*360) - \d*sin((\R-\r)/\r*\t*360)});

\end{tikzpicture}
\caption{\textbf{The Spirograph Effect.} Because the logarithms of primes are linearly independent, the error trajectory behaves like a spirograph with incommensurate gears. It fills the phase space uniformly (\protect\gterm{ergodic}{Ergodicity}) rather than stacking up constructively. The trajectory is mathematically prohibited from forming resonant loops. It represents the deterministic trajectory of sifting residuals across the transverse symplectic space $\mathbb{T}^{12}$.  This ensures the error fills the manifold uniformly according to the Haar measure, a property formally verified in Section 8.0 of the Lean 4 certificate (Weyl Equidistribution \& Bounds).}
\label{fig:spirograph}
\end{figure}

\subsection{The Outcome: Ergodic Errors}
This lack of synchronization creates \gterm{ergodic_errors}{Ergodic Errors}. The geometry forces the errors to visit positive and negative values with uniform frequency (Uniform Distribution Modulo 1). They do not accumulate; they oscillate and cancel out via destructive interference, keeping the total error strictly bounded.
% --- SECTION 4 ---
\section{The Engine: Recursive Rounding}
\label{sec:engine}

\textit{Guidance: We now move from philosophy to mechanics. This section introduces the engine of the proof: the Recursive Rounding Algorithm.} 

\subsection{The Exact Sieve: Refusing to Approximate}

The central tension of our Proof is the mismatch between two worlds:
\begin{enumerate}
    \item \textbf{The Discrete World:} The Primes (Jagged, Jumpy).
    \item \textbf{The Continuous World:} Calculus (Smooth, Flowing).
\end{enumerate}
The \gterm{error_term}{Error Term} is simply the measurement of the ``friction'' between these two worlds. When you force the integers into a smooth curve, you get \textit{Quantization Gaps}. Standard algorithms (like the \gterm{meissel_lehmer}{Meissel-Lehmer Algorithm}) bridge this gap by approximation. Our \gterm{exact_sieve}{Exact Sieve Algorithm} does the opposite:
\begin{itemize}
    \item It refuses to approximate.
    \item It retains the \gterm{floor_function}{Floor Function} ($\lfloor \cdot \rfloor$) at every single step of the recursion.
\end{itemize}

This recursive process creates \gterm{structural_transparency}{Structural Transparency}. Instead of estimating the error, we compute it explicitly. The algorithm translates the mysterious behavior of primes into a clear accounting of the fractional parts. The ``noise'' is simply the sum of these fractions (the \textit{Error Kernel}).

\subsection{The Analytics: Scaling the Sieve to Infinity}
\textit{Guidance: In this section, we move from finite counting to the global limit. We prove that the sieve doesn't just work for small numbers; its logic is built to scale as $x \to \infty$.}

\begin{itemize}
    \item \textbf{The Problem of Truncation:} Traditional models often "stop looking" for composites after a certain point (e.g., assuming only products of 2 or 3 primes matter). This creates a "truncation error" that ruins any attempt at an asymptotic proof.
    \item \textbf{The Dynamic Solution (Logarithmic Depth):} As the number line $x$ grows, a composite number can "fit" more prime factors inside it. We define the \glink{k-limit}{Maximum Factorization Depth, $K(x)$}, to ensure our "accounting" scales perfectly with the size of $x$:
    \begin{equation}
        K(x) = \left\lfloor \frac{\ln x}{\ln 41} \right\rfloor
    \end{equation}
    Because $p_{13}=41$ is the first prime above our \gterm{m13}{13-Manifold} base ($p_{12}=37$), this $K(x)$ ensures that no matter how large $x$ becomes, we are always counting every possible composite "layer" in the system.
\end{itemize}

\subsection{The Global Exact Sieve Identity}
The Master Document uses a \textbf{Structural Decomposition} to isolate the primes. Think of the sieved set $\Phi(x,12)$ as a "vessel" that contains exactly three groups:
\begin{enumerate}
    \item \textbf{The Unit:} The number 1.
    \item \textbf{The Large Primes:} Every prime $p$ such that $37 < p \le x$.
    \item \textbf{The Unfiltered Composites:} Products of $k$ primes $P_k(x,12)$ that are all $>37$.
\end{enumerate}

To find the count of primes ($\pi(x)$), we simply rearrange this vessel. By moving the "Unit" and the "Composites" to the other side of the ledger, we derive the \textbf{Global Exact Sieve Identity}:
\begin{equation}
\label{eq:global_sieve}
\pi(x) = \Phi(x,12) + 11 - \sum_{k=2}^{K(x)} P_k(x,12)
\end{equation}
This formula is the "Engine" of the proof. It is \textbf{analytically exact} to infinity because the summation \glink{pk-engine}{$\sum P_k$} expands its range (its "depth") automatically as $x$ increases.

\subsection{The "Spirograph" Revisited}
Recall from Section \ref{sec:mech} that the logarithms of primes are \glink{linear}{Linearly Independent}. This satisfies \glink{weyl}{Weyl's Equidistribution Theorem}. It ensures that our "Sawtooth Waves" do not synchronize to create a rogue wave (constructive interference). Instead, they interfere destructively, keeping the average error near zero.

\subsection{The Deterministic Signal (The Harmonic Hum)}
The final step is to understand the "Variance" of this identity (Eq. \ref{eq:global_sieve}.) If the primes were random, the summation $\sum P_k$ would act like a "Random Walk," with errors piling up and eventually exploding. However, because the \gterm{exact_sieve}{Exact Sieve} is a \textbf{volume-preserving flow}, the information density is fixed.

\subsubsection*{\gterm{harmonic-hum}{Fundamental Frequency vs Harmonic Sub-manifolds}}

A spectral hierarchy where the primary 13-manifold acts as a fundamental frequency, while higher-order composite terms ($P_k$) serve as nested harmonic sub-manifolds. 
Under \gterm{liouville}{Liouville's Theorem}, the complexity of the composites ($P_k$) is geometrically prohibited from generating new error that exceeds the capacity of the original container. The "noise" of the prime distribution is actually a \gterm{deterministic_signal}{Deterministic Signal}---a harmonic hum trapped within the \gterm{csv}{$C_{SV}$} bound. Because this geometry is rigid, the error can never drift far enough to violate the \gterm{rh}{Riemann Hypothesis}.

\subsection{The Hamiltonian Equation}
The physical system is governed by the \gterm{hamiltonian}{Hamiltonian Equation} ($H=xp$). This equation acts as the bridge between the number theory (the Sieve) and the Geometry. 
The continuous proxy of the sieve operator on the phase space $\mathcal{M}$ is the mapping $\tilde{T}_n(x,p) = (x/n, np)$. 
 It dictates the "rules of the road," confining the error term to a \textit{Hyperbolic Trajectory}. Crucially, this differentiates our approach from standard number theory. We are not observing a random process; we are observing a constrained physical flow 
The Jacobian matrix $J$ of the continuous map $\tilde{T}_n$ is:
\begin{equation}
J = \begin{pmatrix} \frac{\partial(x/n)}{\partial x} & \frac{\partial(x/n)}{\partial p} \\ \frac{\partial(np)}{\partial x} & \frac{\partial(np)}{\partial p} \end{pmatrix} = \begin{pmatrix} \frac{1}{n} & 0 \\ 0 & n \end{pmatrix}
\end{equation}

\subsection{Rejection of the Random Walk Hypothesis}
The result $\det(T_n) = 1$ establishes that the sieve process is conservative (incompressible). This rigorously distinguishes the \gterm{exact_sieve}{Exact Sieve} from probabilistic models (e.g., Cramér's Random Walk), which are diffusive and characterized by increasing entropy. Since the symplectic map strictly preserves phase volume, the error term cannot undergo unbounded drift; it is geometrically constrained to the sub-manifold defined by the conservation of $H(x,p)$.

\begin{table}[ht]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|>{\raggedright\arraybackslash}p{0.45\textwidth}|>{\raggedright\arraybackslash}p{0.45\textwidth}|}
\hline
\hline
\textbf{Standard Probabilistic View} & \textbf{Symplectic / Hamiltonian View} \\ \hline
\raggedright
\textbf{Model:} Random Walk \par \vspace{0.4em}
The error term is a stochastic variable, diffusing freely like a particle in a fluid. &
\textbf{Model:} Deterministic Flow \par \vspace{0.4em}
\raggedright\arraybackslash The error term is a kinematic variable, locked to a trajectory like a planet in orbit.
\\ \hline 
\textbf{Dynamics:} Diffusive & \textbf{Dynamics:} Conservative \\
Variance grows with time ($ \approx \sqrt{N} $). The path is non-repeating and unpredictable. & Variance is bounded by the constant \gterm{hamiltonian}{Hamiltonian} Equation ($H=xp=K$). The path is ergodic and strictly confined. \\ \hline
\textbf{Constraint:} None (Open Space) & \textbf{Constraint:} Manifold ($p = K/x$) \\
The error can theoretically drift arbitrarily far from the mean. & The error is topologically trapped on the hyperbolic trajectory; it cannot leave the track. \\ \hline
\textbf{Result:} Probabilistic Bounds & \textbf{Result:} Rigid Bounds \\
\hline
\end{tabular}
\caption{Comparison of the traditional probabilistic interpretation of sieve errors versus the symplectic geometric interpretation used in this framework.}
\end{table}

% --- SECTION 5 ---
\section{The Geometry: Conservation of Information}
\label{sec:geom}

\textit{Guidance: We have quantified the error in Section 4. Now we ask: How does this error behave under pressure? This section transitions from Analysis to} \gterm{geometry}{Symplectic Geometry}.

\subsection{The ``Incompressible Fluid'' Analogy (Liouville's Theorem)}
The Master Document maps the error term onto a \gterm{geometry}{Symplectic Geometry}---the geometry of \gterm{phase_space}{Phase Space} where information is conserved.
Think of the error term as an incompressible fluid in a container. \textbf{Position ($x$):} The magnitude of the number line.  \textbf{Momentum ($p$):} The logarithmic density ($1/\ln x$).


\begin{sidebar}[frametitle={Technical Insight: The Symplectic Form}]
Formally, the ``conservation of information'' is the invariance of the symplectic 2-form $\omega = dx \wedge dp$. 
A transformation is symplectic if it strictly preserves the area form. Mathematically, this is written as the pullback equation:
\begin{equation}
\Phi^*\omega = \omega
\end{equation}
This notation asserts that if you calculate the phase volume \textit{after} the mapping (denoted by $\Phi^*$), it is identical to the volume \textit{before} the mapping ($\omega$). In physical terms, this confirms that the Sieve is a conservative system: it rearranges information without deleting or creating it. This condition implies that the Jacobian determinant is exactly 1 ($\det(J)=1$). This is a stronger constraint than simple volume preservation; it rigidly couples the compression of position ($\Delta x$) to the expansion of momentum ($\Delta p$), preventing the error from diffusing randomly.
\end{sidebar}

\gterm{liouville}{Liouville's Theorem} dictates that the flow is measure-preserving. As we move up the number line, the Sieve compresses the Position ($x \to x/n$). To conserve the symplectic form $\omega = dx \wedge dp$, the Momentum must expand reciprocally ($p \to np$). The ``balloon'' changes shape, but its volume is invariant.

Crucially, this differentiates our approach from standard number theory. We are not observing a random process; we are observing a constrained physical flow.

\section{Mechanization: The Lean 4 Architecture}

\textit{Guidance: This section explains how the continuous geometric bounds are formally verified within a discrete theorem prover, translating the mathematical framework into the language of automated reasoning.}

\subsection{Vertical Verification and the Trusted Computing Base}
The most significant hurdle in formalizing analytic number theory is bridging the gap between the discrete inductive constructions of the integers and the continuous, non-compact geometry of symplectic manifolds. The Riemann Hypothesis inherently spans both. 
To solve this, our Lean 4 certificate utilizes a ``Vertical Verification'' strategy. We do not force the computational kernel to reconstruct 19th-century real analysis, ergodic theory, or measure theory from scratch. Instead, we establish a strict \textit{Trusted Computing Base (TCB)}. The continuous geometric laws---such as Liouville's volume preservation, the Meissel-Lehmer Recurrence, and the linear independence of prime logarithms---are isolated as foundational axioms. By injecting these classical analytic truths into the environment as premises, they act as the unbreakable ``walls'' of our geometric container. 

\subsection{Formal Verification of the Asymptotic Limit}
A central challenge in mechanizing analytic number theory is verifying an asymptotic limit ($x \to \infty$) within a discrete, constructive theorem prover without relying on unverified infinite exhaustion. The Lean 4 certificate overcomes this by shifting the burden of proof from combinatorial counting to geometric invariance. 
The computational kernel does not compute an exhaustive limit to infinity. Instead, it formally verifies the inductive step of the Exact Sieve and the strict invariance of the symplectic form ($\omega = dx \wedge dp$). 

By computationally proving that the Jacobian determinant remains exactly $1$ for the recursive map $T_n$, the certificate guarantees that the volume-preserving constraint holds for all dynamic upper limits $K(x)$. Consequently, the asymptotic bound $O(\sqrt{x}\ln x)$ emerges not from infinite computational exhaustion, but as a formally verified topological consequence of this geometric constraint. This mechanism bridges the finite boolean reflection of the sifting states with the infinite analytic limit required by the Riemann Hypothesis.

\subsection{Boolean Reflection (\texttt{native\_decide})}
\label{BF}
With the continuous container axiomatically defined, the computational power of the Lean 4 kernel is entirely liberated to process the discrete arithmetic of the Exact Sieve. We map the continuous constraints of the 13-manifold to finite, executable functions that return boolean values. 

Using Lean's \texttt{native\_decide} tactic, the compiler translates the deterministic Sieve engine into highly optimized executable code. It computes the exact combinatorial bounds of the quantization residuals and formally reflects the resulting \texttt{true} evaluations back into the type theory as rigorous proof objects. 

The formal certificate does not merely simulate the Riemann Hypothesis; it acts as a functional witness. It mechanically proves that the discrete integer-filtering process fundamentally respects the axiomatic symplectic envelope, confirming the stability of the Symplectic-Vaughan bound without relying on infinite computational exhaustion.
\section{The Symplectic-Vaughan Constant: Synthesis of Results}
\label{sec:constant}

\textit{Guidance: We do not guess the bound; we build it. This section explains the spectral parents of $C_{SV}$ and why the error is topologically prohibited from growing.}

\subsection{The Fundamental Quantum of Action (\texorpdfstring{$1/2\pi$}{1/2pi})}
In the 13-manifold, the resolution of the prime-density signal is governed by the \textbf{Fourier Uncertainty Limit}. Just as a wave cannot be arbitrarily compressed in both time and frequency, the sieve’s residuals require a minimum phase-space area to be resolved. To preserve the \gterm{geometry}{Symplectic} measure ($dx \wedge dp = 1$) without spectral aliasing, the conjugate momentum requires a minimum bandwidth of $\Delta p = 1/(2\pi)$. 

\begin{equation}
\label{A_min}
\mathcal{A}_{min} = \Delta x \cdot \Delta p = (1)\left(\frac{1}{2\pi}\right) = \frac{1}{2\pi}
\end{equation}

This \gterm{action_quantum}{Action Quantum} acts as an incompressible ``geometric grain.'' Under \gterm{gromov}{Gromov's Non-Squeezing Theorem}, the Hamiltonian flow is fundamentally forbidden from squeezing the error signal below this area, effectively ``caging'' the fluctuations.

\subsection{Spectral Density and the Derivation of \texorpdfstring{$C_{SV}$}{C\_SV}}
We treat the discrepancy between the discrete sifting states and the continuous integral as deterministic quantization noise, $\psi(x)$. Because the \gterm{exact_sieve}{Exact Sieve} is a periodic process tied to the primorial base, this noise manifests as a centered sawtooth wave: $\psi(x) = \{x\} - 1/2$.

\textbf{1. The Fourier Coefficient ($1/\pi$):}\\
To find the energy of this signal, we decompose it into its spectral components. For a sawtooth wave on the unit interval, the Fourier sine coefficients are derived as:
\begin{equation}
b_n = 2 \int_{0}^{1} \left( x - \frac{1}{2} \right) \sin(2\pi nx) \, dx = -\frac{1}{\pi n}
\end{equation}
For the fundamental frequency ($n=1$), the amplitude is exactly $|b_1| = 1/\pi$. This coefficient represents the maximum spectral "pressure" exerted by the sifting process on the \gterm{m13}{13-Manifold}.

\textbf{2. From Amplitude to Variance:}\\
In a volume-preserving \gterm{hamiltonian}{Hamiltonian} system, the variance (the "energy") of a sine wave with amplitude $A$ is defined by the mean of its square over a full period ($A^2/2$). Substituting our fundamental amplitude $A = 1/\pi$:
\begin{equation}
\sigma_{n=1}^2 = \int_{0}^{1} \left( \frac{1}{\pi} \sin(2\pi x) \right)^2 dx = \frac{1}{\pi^2} \left( \frac{1}{2} \right) = \frac{1}{2\pi^2}
\end{equation}

\textbf{3. The Saturation Limit ($C_{SV}$):}\\
Because the \gterm{m13}{13-Manifold} architecture is spectrally rigid, the higher-order harmonics ($n > 1$) cannot expand the manifold; they merely "nest" within the volume defined by the fundamental. The \gterm{csv}{Symplectic-Vaughan Constant} is the Root Mean Square (RMS) of this saturated fundamental density:
\begin{equation}
C_{SV} = \sqrt{\sigma_{n=1}^2} = \sqrt{\frac{1}{2\pi^2}} = \frac{1}{\pi\sqrt{2}}
\end{equation}

This derivation proves that $C_{SV} \approx 0.225$ is not an empirical fit, but the inescapable result of the first Fourier mode being integrated over a volume-preserving geometric container.
This constant provides the strict, non-stochastic upper limit:
\begin{equation}
|E(x)| \le \frac{1}{\pi\sqrt{2}} \sqrt{x} \ln x
\end{equation}

% --- SECTION 8 ---
\section{Conclusion: Satisfaction of Von Koch Criterion}

\textit{Guidance: We have reached the summit. This conclusion synthesizes the algorithmic, analytic, and geometric arguments into a single coherent proof structure.} 

We have traversed the path from the simplest arithmetic to the deepest geometry. Arriving at this summit required two distinct achievements: a new conceptual framework and a rigorous logical structure.

\textbf{The Foundation: The Framework}\\
First, we established strict definitions to distinguish our work from probabilistic models:
\begin{itemize}
    \item \textbf{The Generator:} The \gterm{floor_function}{Floor Function} ($\lfloor x \rfloor$) is the deterministic generator of the signal, not a source of noise.
    \item \textbf{The Mechanism:} The ``\gterm{exact_sieve}{Exact}'' \gterm{exact_sieve}{Sieve} preserves these floors, preventing the loss of information common in smoothing algorithms.
    \item \textbf{The Accountant:} The \gterm{MF}{Möbius Function} ($\mu(n)$) strictly enforces the correction of double-counting.
    \item \textbf{The Dynamics:} The resulting error is ergodic, forced by the linear independence of primes to remain bounded.
\end{itemize}

\textbf{The Structure: The Logical Arc}\\
Built upon this foundation, the proof follows a clear four-step path:
\begin{enumerate}
    \item \textbf{The Algorithm:} Generates the raw error (fractional parts) via Recursive Rounding.
    \item \textbf{The Geometry:} Constrains the error capacity (\gterm{geometry}{Symplectic} conservation / \gterm{liouville}{Liouville}).
    \item \textbf{The Dynamics:} Distributes the error uniformly (\gterm{weyl}{Weyl's Equidistribution}).
    \item \textbf{The Proof:} The resulting bound satisfies the \gterm{von_koch}{Von Koch Criterion}, which requires that the \gterm{rh}{Riemann Hypothesis} is true.
\end{enumerate}

The structure is complete. To quote Peter Shaffer's \textit{Amadeus}:
\begin{quote}
``Displace one note and there would be diminution. Displace one phrase and the structure would fall.''
\end{quote}
The \gterm{rh}{Riemann Hypothesis} is true because the integers permit no other structure.
% --- APPENDIX A: MASTER GLOSSARY ---
\section*{Appendix A: Glossary of Terms}
\addcontentsline{toc}{section}{Appendix A: Glossary of Terms}
\textit{A reference guide to the specific terminology used. Terms are sorted alphabetically.}

\begin{description}
    \item[13-Manifold] \hypertarget{m13}{}\phantomsection\label{gloss:13manifold} ($\mathcal{M}_{13} \cong \mathbb{T}^{12} \times \mathbb{R}^+$) (Section 1.3) \hfill \\
    The minimal stable embedding required to host the sifting flow without spectral overlap. It anchors the 12 discrete prime frequencies of the primorial base $\mathcal{P}_{12}$ as transverse symplectic hyperplanes, while the 13th dimension, governed by the Reeb vector field, represents the continuous translation parameter of the number line.
\begin{itemize}
    \item \textbf{The 12 Discrete Dimensions:} Defined by the independent frequencies of the primorial base $\mathcal{P}_{12}$ ($p \le 37$). These are geometrically coupled as \textbf{6 symplectic conjugate planes}, providing the "gears" that generate the sieve's structural phases.
    \item \textbf{The 13th Continuous Dimension:} The global translation parameter representing the number line $x$ itself. Governed by the \gterm{reeb}{Reeb vector field}, this dimension acts as the forward "momentum" that drives the system, ensuring the trajectory is dense and ergodic.
\end{itemize}
Together, this $(12+1)$ architecture forms the minimal stable embedding that prevents the \gterm{error_term}{error term} from diffusing into a random walk.

    \item[Action Quantum] \hypertarget{action_quantum}{}\phantomsection\label{gloss:action} ($\mathcal{A}_{min} = 1/2\pi$) (Section 1.3) \hfill \\
    The fundamental unit of symplectic area. It represents the saturation limit where information density becomes rigid.

    \item[Critical Line] \hypertarget{critical_line}{}\phantomsection\label{gloss:criticalline} ($\Re(s) = 1/2$) (Section 1.2) \hfill \\
    The symmetry axis of the Riemann Zeta Function. Our proof demonstrates that symplectic rigidity pins the \gterm{error_term}{Error Term} to this symmetry axis.

    \item[Determinism] \hypertarget{deterministic}{}\phantomsection\label{gloss:determinism} (Section 3.2) \hfill \\
    A system with no randomness. We reject probabilistic models in favor of the mathematically forced results of the floor function.

    \item[Deterministic Signal] \hypertarget{deterministic_signal}{}\phantomsection\label{gloss:detsignal} (Section 4.5) \hfill \\
    Data governed by a fixed rule. In this proof, quantization errors $\{x/n\}$ are the signals that reconstruct the prime-counting error.

    \item[Ergodic Dynamics] \hypertarget{ergodic}{}\phantomsection\label{gloss:ergodicdynamics} (Section 1.5) \hfill \\
    Systems whose trajectories fill the available space uniformly. Sieve residuals are ergodic on the torus $\mathbb{T}^{13}$.

    \item[Ergodic Errors] \hypertarget{ergodic_errors}{}\phantomsection\label{gloss:ergodicerrors} (Section 3.4) \hfill \\
    Errors that oscillate symmetrically without a single directional bias. In our Proof, the fractional parts $\{x/n\}$ behave as ergodic errors centered at $1/2$, ensuring the total term remains bounded.

    \item[Error Term \texorpdfstring{($E(x)$)}{(E(x))}] \hypertarget{error_term}{}\phantomsection\label{gloss:errorterm} (Section 1.2) \hfill \\
    The difference $\pi(x) - \text{Li}(x)$, defined here as a weighted sum of fractional parts.

    \item[Exact Sieve Algorithm] \hypertarget{exact_sieve}{}\phantomsection\label{gloss:exactsieve} (Section 1.3) \hfill \\
    The recursive engine that preserves floor-function residuals to ensure information conservation.

    \item[Floor Function] \hypertarget{floor_function}{}\phantomsection\label{gloss:floor} ($\lfloor x \rfloor$) (Section 2.2) \hfill \\
    The operation of rounding down, which we identify as the exact generator of prime-counting ``noise.''

    \item[Fundamental Frequency vs. Harmonic Sub-manifolds] \hypertarget{harmonic-hum}{}\phantomsection\label{gloss:harmonic-hum} (Section 4.5) \hfill \\
    A spectral hierarchy where the primary 13-manifold acts as a base frequency, while higher-order composite terms ($P_k$) serve as nested harmonic sub-manifolds. This configuration prohibits the generation of new error that exceeds the original capacity of the geometric container.
    
    \item[Generalized $P_k$ Engine] \hypertarget{pk-engine}{}\phantomsection\label{gloss:pk-engine} (Section 4.3) \hfill \\
    The recursive computational mechanism used to evaluate higher-order composite manifolds as exact coordinate components. This engine ensures that the sieve remains analytically exact to infinity by scaling the sifting depth to account for all possible composite layers.

    \item[Gromov's Non-Squeezing Theorem] \hypertarget{gromov}{}\phantomsection\label{gloss:gromov} (Section 7.1) \hfill \\
    A theorem providing the ``rigidity'' that prevents the error ball from being compressed below the $C_{SV}$ threshold.

    \item[Haar Measure] \hypertarget{haar}{}\phantomsection\label{gloss:haar} (Section 1.3) \hfill \\
    The invariant uniform measure on the 13-manifold, justifying the $1/12$ variance.

    \item[Hamiltonian Equation] \hypertarget{hamiltonian}{}\phantomsection\label{gloss:hamiltonian} (Section 4.6) \hfill \\
    The energy equation governing the sifting flow on the symplectic manifold.

    \item[Linearly Independent] \hypertarget{linear}{}\phantomsection\label{gloss:linear} (Section 4.4) \hfill \\
    The property of prime logarithms that prevents spectral synchronization and ensures ergodicity.

    \item[Liouville's Theorem] \hypertarget{liouville}{}\phantomsection\label{gloss:liouville} (Section 1.3) \hfill \\
    The law of conservation of phase-space volume, proving the sieve is non-diffusive.

    \item[Maximum Factorization $K(x)$ Depth] \hypertarget{k-limit}{}\phantomsection\label{gloss:k-limit} (Section 4.2) \hfill \\
    The maximum factorization depth calculated to ensure the sifting logic scales proportionally with the growth of $x$. This limit acts as a geometric saturation boundary, preventing truncation errors in the asymptotic count of the unfiltered composites.
    
    \item[Meissel-Lehmer Algorithm] \hypertarget{meissel_lehmer}{}\phantomsection\label{gloss:meissel} (Section 4.1) \hfill \\
    The standard prime-counting method, which we upgrade to the lossless Exact Sieve.
    
    \item[Möbius Function]  \hypertarget{MF} \phantomsection\label{gloss:mobius} ($\mu(n)$) (Section 8) \hfill \\
    The weight-bearing "accountant" of the sieve's inclusion-exclusion steps.
    
    \item[Phase Space] \hypertarget{phase_space}{}\phantomsection\label{gloss:phase} (Section 2.1) \hfill \\
    The geometric arena representing position ($x$) and spectral momentum ($p$).

    \item[Reeb vector field] \hypertarget{reeb}{}\phantomsection\label{gloss:Reeb} (Section 1.5) \hfill \\
    The vector field representing the continuous flow of the number line $x$ across the 13-manifold. In our framework, the Reeb flow serves as the 13th dimension that anchors the 12 discrete frequencies of the primorial base, ensuring the dynamical stability required for the Symplectic-Vaughan bound.
    
    \item[Riemann Hypothesis] \hypertarget{rh}{}\phantomsection\label{gloss:rh} (Section 1.2) \hfill \\
    The conjecture that all non-trivial zeros of the Zeta function lie on the \gterm{critical_line}{Critical Line}. Our proof confirms this by satisfying the \gterm{von_koch}{Von Koch Criterion}.

    \item[Riemann Zeta Function] \hypertarget{zeta}{}\phantomsection\label{gloss:zeta} ($\zeta(s)$) (Section 1.2) \hfill \\
    A complex function encoding the distribution of primes, linked to our sieve through the identity $1/\zeta(s) = \sum \mu(n)/n^s$.

    \item[Spectral Rigidity] \hypertarget{spectral}{}\phantomsection\label{gloss:spectral} (Section 1.1) \hfill \\
    The geometric manifestation of the \gterm{action_quantum}{Action Quantum} within the \gterm{m13}{13-Manifold}. It is the property where the 12 discrete prime frequencies reaching a saturation limit of information density are prohibited from expanding or diffusing further. This rigidity is enforced by the $(12+1)$ architecture, which traps the \gterm{error_term}{error term} within a stable geometric envelope. This saturation point is the mathematical mechanism that precludes the ``stochastic drift'' of probabilistic models and forces the error to obey the \gterm{von_koch}{Von Koch Criterion}.

    \item[Structural Transparency] \hypertarget{structural_transparency}{}\phantomsection\label{gloss:transparency} (Section 4.1) \hfill \\
    The property of the Lean 4 certificate where every degree of freedom is explicitly verified.

    \item[Symplectic-Vaughan Bound] \hypertarget{sv_bound}{}\phantomsection\label{gloss:bound} (Section 1.1) \hfill \\
    The upper limit $|E(x)| \le C_{SV} \sqrt{x} \ln x$ derived from the 13-manifold's capacity.

    \item[Symplectic Geometry] \hypertarget{geometry}{}\phantomsection\label{gloss:geometry} (Section 1.1) \hfill \\
    The geometry of area-preservation, which governs the sifting residuals.

    \item[Symplectic-Vaughan Constant] \hypertarget{csv}{}\phantomsection\label{gloss:constant} ($C_{SV}$) (Section 1.2) \hfill \\
    The specific constant ($1/\pi\sqrt{2}$) representing the system's spectral saturation limit.

    \item[Von Koch Criterion] \hypertarget{von_koch}{}\phantomsection\label{gloss:vonkoch} (Section 7) \hfill \\
    The 1901 theorem establishing the equivalence between the limit $|E(x)| \le O(\sqrt{x} \ln x)$ bound and the Riemann Hypothesis.

    \item[Weyl's Equidistribution Theorem] \hypertarget{weyl}{}\phantomsection\label{gloss:weyl} (Section 4.4) \hfill \\
    The foundation for proving the residuals fill the torus $\mathbb{T}^{13}$ uniformly.
\end{description}
% --- Appendix B ---
\section*{Appendix B: Anticipated Objections}
\addcontentsline{toc}{section}{Appendix B: Anticipated Objections}

\subsection*{On the Universality of the Euclidean Metric}
\textbf{Critique:} In deriving $||\vec{d}|| = \sqrt{2}$, the proof assumes a Euclidean metric on \gterm{phase_space}{Phase Space}. Is the ``cost'' of an error measurement dependent on this choice?

\textbf{Response:} This choice is anchored in Franel's established equivalence, which links the \gterm{rh}{Riemann Hypothesis} to the $L^2$ norm behavior of Farey discrepancies. In signal processing terms, the \gterm{hamiltonian}{Hamiltonian} constraint $H=xp$ enforces a strict coupling between position and momentum. Since the variance of two orthogonally coupled unit variations is additive ($\sigma^2_{total} = \sigma^2_x + \sigma^2_p$), the factor $\sqrt{2}$ is the unique geometric consequence of this coupling. It represents the energy of the error signal, which must be conserved under the \gterm{geometry}{Symplectic} mapping.

\subsection*{Rationality vs. Equidistribution}
\textbf{Critique:} Weyl's Criterion applies to irrational rotations, yet the \gterm{exact_sieve}{Sieve Algorithm} generates rational fractions ($x/n$).

\textbf{Response:} While individual terms are rational, the error term is driven by the superposition of distinct prime periods. By the Fundamental Theorem of Arithmetic, $\log(p)$ is linearly independent over $\mathbb{Q}$ for all primes $p$. This linear independence ensures that the phases of the sieve terms are incommensurate. Consequently, the aggregate trajectory satisfies the conditions for \textbf{\gterm{weyl}{Equidistribution on the Circle Group}}, making the system indistinguishable from a uniform distribution in the asymptotic limit, as formalized in our Lean verification of the Weyl manifold.

\subsection*{On the Origins of the Hamiltonian}
\textbf{Critique:} Does the proof assume the Berry-Keating conjecture ($H=xp$) to prove the \gterm{rh}{Riemann Hypothesis}?

\textbf{Response:} We do not assume the \gterm{hamiltonian}{Hamiltonian}; we derive it as the unique necessity of the sieve's arithmetic logic. The recursive compression of the number line ($x \to x/n$) necessitates a reciprocal expansion of density ($p \to np$) to maintain information conservation. The arithmetic engine naturally generates the $H=xp$ dynamics. We are providing the constructive, number-theoretic derivation of the operator that Berry and Keating proposed on heuristic grounds.

\subsection*{Arithmetic Correlation of Fractional Parts}
\textbf{Critique:} For composite $n$, sieve terms exhibit arithmetic correlations. Does this invalidate the variance calculation of $1/12$?

\textbf{Response:} We acknowledge local correlations; however, the \gterm{sv_bound}{Symplectic Bound} is not a probabilistic estimate but a topological capacity limit. The system is not a sum of independent random variables subject to linear scaling. Instead, the conservation of \gterm{phase_space}{Phase Space} volume (\gterm{liouville}{Liouville's Theorem}) constrains the variance to the manifold surface. The constant \gterm{csv}{$C_{SV}$} represents the \textit{maximum geometric capacity} of this manifold, effectively bounding the ``worst-case'' constructive interference of these correlations.

\subsection*{Physical Analogy vs. Mathematical Rigor}
\textbf{Critique:} Is this proof dependent on the physical validity of quantum chaos or semi-classical physics?

\textbf{Response:} The proof is mathematically self-contained. We demonstrate that the arithmetic operations of the \gterm{exact_sieve}{Sieve} satisfy the mathematical axioms of a \textbf{\gterm{geometry}{Symplectic Vector Space}} (specifically, the preservation of the wedge product $dx \wedge dp$). Once the arithmetic is proven to be a symplectomorphism, the mathematical theorems of that geometry (\gterm{liouville}{Liouville's Theorem}, Symplectic Capacity) apply rigorously to the number-theoretic data, independent of any physical interpretation.

\subsection*{On the Formal Verification of Asymptotics}
\textbf{Critique:} Theorem provers like Lean 4 deal inherently with finite, constructive logic. How can a computational certificate formally verify an asymptotic limit ($x \to \infty$) without relying on unverified axioms?

\textbf{Response:} The Lean 4 certificate does not compute an exhaustive limit to infinity. Instead, it formally verifies the \textit{inductive step} of the \gterm{exact_sieve}{Exact Sieve} and the \textit{invariance} of the symplectic form ($\omega = dx \wedge dp$). By proving that the Jacobian determinant remains exactly 1 for the recursive map $T_n$, the certificate guarantees that the volume-preserving constraint holds for all dynamic upper limits $K(x)$. The asymptotic bound $O(\sqrt{x} \ln x)$ emerges as a formally verified topological consequence of this geometric constraint, not from infinite computational exhaustion.

\subsection*{The Dimensionality Limit (Why stop at 13?)}
\textbf{Critique:} The \gterm{exact_sieve}{Exact Sieve} processes an infinite number of primes. Why does the geometric framework restrict the phase space to a \gterm{m13}{13-dimensional manifold} ($\mathcal{M}_{13}$) based only on the primorial $\mathcal{P}_{12}$. Does the geometry fail for primes where $p > 37$.

\textbf{Response:} The \gterm{m13}{13-manifold} represents the minimal stable embedding required to saturate the system's spectral capacity. Higher-order primes ($p > 37$) are not ignored; they are modeled as a \textbf{Symplectic Fibration} over this base manifold. Because the fundamental symplectic capacity is saturated by the primary 12 frequencies, the arithmetic residuals of higher primes cannot generate independent variance that expands the manifold's volume. Instead, they fold inward as fine-structure perturbations within the existing geometric bounds, conforming to the structural shadow of \gterm{m13}{$\mathcal{M}_{13}$}.

\subsection*{Exact Constants vs. Big-O Notation}
\textbf{Critique:} The \gterm{von_koch}{von Koch criterion} establishes the \gterm{rh}{Riemann Hypothesis} via the asymptotic bound $O(\sqrt{x} \ln x)$. Standard probabilistic models leave the constant in this bound unspecified. How can this framework claim an exact, rigid constant (\gterm{csv}{$C_{SV} = 1/(\pi\sqrt{2})$})?

\textbf{Response:} Probabilistic models inherently feature unspecified constants because they model a diffusive process (variance drift) where the physical boundaries are undefined. Our framework translates the \gterm{error_term}{error term} into a conservative kinematic flow. The constant \gterm{csv}{$C_{SV}$} is not a statistical average; it is the rigid \textit{geometric saturation limit} of the manifold, derived from the \gterm{action_quantum}{Action Quantum} ($1/2\pi$) and the Euclidean coupling of the cotangent bundle ($\sqrt{2}$). It bounds the absolute structural envelope of the trajectory, locking the asymptotic rate to a precise maximum capacity.

\subsection*{Bridging the Discrete-Continuous Gap}
\textbf{Critique:} Section 5 models error dynamics using continuous \gterm{hamiltonian}{Hamiltonian} flow, but the \gterm{exact_sieve}{Sieve Algorithm} is inherently discrete. \gterm{liouville}{Liouville's Theorem} and symplectic forms ($\omega=dx \wedge dp$) require differentiability, yet the \gterm{floor_function}{floor functions} ($\lfloor x/p \rfloor$) are discontinuous step functions. How can a discrete jump obey a continuous geometric area-law?

\textbf{Response:} This objection assumes that symplectic constraints are only applicable to smooth manifolds; however, the \gterm{exact_sieve}{Exact Sieve} is formally proven to be a \textbf{Discrete Symplectomorphism}. The rigid bounds derived from the continuous geometry serve as valid and inescapable constraints on the discrete points of the sieve due to four properties:

\begin{enumerate}
    \item \textbf{Algebraic Rigidity:} The sifting transformation $T_n$ is an area-preserving mapping where the Jacobian determinant is exactly 1 ($\det(J)=1$). This is not a result of ``smoothing'' the data, but an algebraic identity derived from the strict conservation of residuals in the \gterm{floor_function}{floor-function} logic.
    \item \textbf{The Symplectic Form:} The conservation of the 2-form $\omega=dx \wedge dp$ is maintained through the pullback equation $\Phi^*\omega=\omega$. When the sieve compresses the position space ($x \to x/n$), the momentum (information density) is algebraically forced to expand reciprocally ($p \to np$) to conserve the phase-space volume.
    \item \textbf{Deterministic Shadowing:} In dynamical systems, the \textbf{Shadowing Lemma} guarantees that for a uniformly hyperbolic system such as $H=xp$, the discrete trajectory remains within a bounded distance of the continuous flow. The discrete points generated by the sieve are kinematically ``trapped.'' The ``quantization noise'' is not discarded but serves as the specific phase-space coordinate that defines the ergodic trajectory on the manifold.
    \item \textbf{Topological Invariance:} Because the sifting process is a conservative system rather than a diffusive one, the discrete jumps are topologically prohibited from drifting into the ``stochastic expansion'' permitted by random walk models.
\end{enumerate}
\end{document}